Parsing Postfix Log Files

### 2009-08-27 doc/logparser-implementation.tex
Improvements to the flow chart, required by Howard Hamilton.

Everything starts off with a mail entering the system, whether by local
submission via \daemon{postdrop}, by \acronym{SMTP}, by re-injection
because of forwarding, or generated internally by Postfix.  Local
submission is the simplest of the four: a queueid is assigned immediately
\flowchart{PICKUP}{2}, and the mail moves on to the delivery stage.
Re-injection because of forwarding lacks explicit log lines of its own; it
is explained fully in \sectionref{Re-injected mails}.  Internally generated
mails lack any explicit origin in Postfix 2.2.x and must be detected using
heuristics as described in \sectionref{identifying bounce notifications};
later versions of Postfix do provide log lines for internally generated
mails \flowchart{BOUNCE\_CREATED}{3}.  Bounce notifications are the primary
example of internally generated mails, though other types exist, e.g.\
Postfix may generate mails to the administrator when it encounters
configuration errors.

@@

    \item The client disconnects \flowchart{DISCONNECT \textnormal{or}
        TIMEOUT}{6}, either normally or with an error.  If Postfix has
        rejected any mail delivery attempts the data gathered from those
        rejections will be saved to the database \flowchart{DISCONNECT}{7};
        if there were no rejections there will not be any data to save.
        Any mails accepted will already have been cloned so their data is
        in another data structure, and will be delivered in the same way as
        mails that entered the system by any other route.

>>>>

Everything starts off with a mail entering the system, whether by local
submission via \daemon{postdrop} or \daemon{sendmail}, by \acronym{SMTP},
by re-injection because of forwarding, or generated internally by Postfix.
Local submission is the simplest of the four: a queueid is assigned
immediately \flowchart{PICKUP}{2}, and the mail moves on to the delivery
stage.  Re-injection because of forwarding lacks explicit log lines of its
own; it is explained fully in \sectionref{Re-injected mails}.  Internally
generated mails lack any explicit origin in Postfix 2.2.x and must be
detected using heuristics as described in \sectionref{identifying bounce
notifications}; later versions of Postfix do provide log lines for
internally generated mails \flowchart{BOUNCE\_CREATED}{3}.  Bounce
notifications are the primary example of internally generated mails, though
other types exist, e.g.\ Postfix may generate mails to the administrator
when it encounters configuration errors.

@@

    \item The client disconnects \flowchart{DISCONNECT \textnormal{or}
        TIMEOUT}{6}, either normally or with an error.  If Postfix has
        rejected any mail delivery attempts the data gathered from those
        rejections will be saved to the database \flowchart{DISCONNECT}{7};
        if there were no rejections there will not be any data to save.
        Any accepted mails will already have a separate data structure, and
        will be delivered in the same way as mails that entered the system
        by any other route.
